Detecting Hand Direction for Computer Interaction

### 2014-12-10 paper/paper.tex
Paper edits mostly. Fixing bugs in evaluation.

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{gensymb}

@@

\begin{figure*}
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
		\includegraphics[height=140px]{figures/PointImage.png}
		\includegraphics[height=140px]{figures/PointHOG.png}
	\end{center}
	\caption{An image (on the left) and our corresponding HOG output (on the right). The location calculated by our algorithm is illustrated by the blue dot on the left image.}
	\label{fig:pointImages}
\end{figure*}

@@

\subsection{Classifier}
We experimented with several different classifiers including k-Nearest Neighbors, linear regression, and SVM. We found that a combination of k-nearest neighbors and linear regression worked best across a wide variety of data. We trained the k-nearest neighbors and linear regression models from sci-kit learn separately on 15 sets of test data comprised of the HOG features computed from each image. These models each predicted a location based on HOG input. These locations were averaged together and fed into a smoothing algorithm to compute the final location.

\subsection{Smoothing}
In order to make the system more robust to noise, we both smooth the location and eliminate outliers. Let $x[n]$ be the location at frame $n$ and $u[n]$ be the location output from the k-NN and linear regression combination at frame $n$. Outliers are eliminated if
\begin{equation}
	\sqrt{\sum_{i=n-l}^{n}(u[n]-x[i])^2} >= \epsilon
\end{equation}
where $l$ and $\epsilon$ are parameters representing the amount of history to remember for computing outliers and the sensitivity to outliers, respectively. We used $l=10$ and $\epsilon=200$. Smoothing is implemented by the formula 
\begin{equation}
	x[n+1] = \left\{
		\begin{array}{l l}
			\lambda x[n] + (1-\lambda)u[n] & \qquad \text{if not an outlier} \\
			x[n] & \qquad \text{otherwise}
		\end{array}
	\right.
\end{equation}
 where $\lambda$ is a smoothing parameter between 0 and 1. We used $\lambda=0.5$ to balance quick responsiveness with robustness to noise.

@@

\subsubsection{Performance of Different Classifiers}
We evaluated the performance of both convolution neural networks and HOG with k-Nearest Neighbors and Linear Regression. The results from our tests our given in figure \ref{fig:hist}, which is a histogram of the error of the different classifiers. The error is the euclidean distance measured in pixels between the predicted point and the actual point.
\begin{figure*}
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
		\includegraphics[width=0.9\linewidth]{figures/ClassifierErrorHist.png}
	\end{center}
	\caption{An image (on the left) and our corresponding HOG output (on the right). The location calculated by our algorithm is illustrated by the blue dot on the left image.}
	\label{fig:hist}
\end{figure*}
\subsection{Evaluation as a Computer Interaction Device}

>>>>

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{gensymb}

@@

\begin{figure}[t]
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
		\begin{subfigure}[b]{0.45\linewidth}
			\includegraphics[width=\linewidth]{figures/PointImage.png}
			\caption{} % Just to get the (a)
		\end{subfigure}
		\begin{subfigure}[b]{0.45\linewidth}
			\includegraphics[width=\linewidth]{figures/PointLeft2Image.png}
			\caption{}
		\end{subfigure}
		\begin{subfigure}[b]{0.45\linewidth}
			\includegraphics[width=\linewidth]{figures/PointHOGedit.png}
			\caption{}
		\end{subfigure}
		\begin{subfigure}[b]{0.45\linewidth}
			\includegraphics[width=\linewidth]{figures/PointLeft2HOGedit.png}
			\caption{}
		\end{subfigure}
	\end{center}
	\caption{An image (on the left) and our corresponding HOG output (on the right). The location calculated by our algorithm is illustrated by the blue dot on the left image.}
	\label{fig:pointImages}
\end{figure}

@@

\subsection{Regression}
We experimented with several different including k-Nearest Neighbors and linear regression. We found that a combination of k-nearest neighbors worked best across a wide variety of data. We trained the k-nearest neighbors and linear regression models from sci-kit learn separately on 15 sets of test data comprised of the HOG features computed from each image. These models each predicted a location based on HOG input. These locations were averaged together and fed into a smoothing algorithm to compute the final location.

\subsection{Smoothing}
In order to make the system more robust to noise, we both smooth the location and eliminate outliers. Let $x[n]$ be the location at frame $n$ and $u[n]$ be the location output from the k-NN and linear regression combination at frame $n$. Outliers are eliminated if
\begin{equation}
	\sqrt{\sum_{i=n-l}^{n}(u[n]-x[i])^2} \geq \epsilon
\end{equation}
where $l$ and $\epsilon$ are parameters representing the amount of history to remember for computing outliers and the sensitivity to outliers, respectively. We used $l=10$ and $\epsilon=200$. Smoothing is implemented by the formula 
\begin{equation}
	x[n+1] = \left\{
		\begin{array}{l l}
			\lambda x[n] + (1-\lambda)u[n] & \qquad \text{if not an outlier} \\
			x[n] & \qquad \text{otherwise}
		\end{array}
	\right.
\end{equation}
 where $\lambda$ is a smoothing parameter between 0 and 1. We used $\lambda=0.5$ to balance quick responsiveness with robustness to noise.

@@

\subsubsection{Performance of Different Regressions}
We evaluated the performance of both convolution neural networks and HOG with k-Nearest Neighbors and Linear Regression. The results from our tests our given in figure \ref{fig:hist}, which is a histogram of the error of the different classifiers. The error is the euclidean distance measured in pixels between the predicted point and the actual point.
\begin{figure*}
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
		\includegraphics[width=0.9\linewidth]{figures/ClassifierErrorHist.png}
	\end{center}
	\caption{}
	\label{fig:hist}
\end{figure*}

\begin{figure*}
	% Figure on bad images
	\begin{center}
		\begin{subfigure}[b]{0.4\textwidth}
			\includegraphics[width=\textwidth]{figures/PointLeftImage.png}
			\caption{} % Just to get the (a)
			\label{fig:pointLeftImage}
		\end{subfigure}
		\begin{subfigure}[b]{0.4\textwidth}
			\includegraphics[width=\textwidth]{figures/PointRightImage.png}
			\caption{}
			\label{fig:pointRightImage}
		\end{subfigure}
		\begin{subfigure}[b]{0.4\textwidth}
			\includegraphics[width=\textwidth]{figures/PointLeftHOG.png}
			\caption{}
			\label{fig:pointLeftHog}
		\end{subfigure}
		\begin{subfigure}[b]{0.4\textwidth}
			\includegraphics[width=\textwidth]{figures/PointRightHOG.png}
			\caption{}
			\label{fig:pointRightHog}
		\end{subfigure}
	\end{center}
	\caption{Examples of images in which our algorithm does not perform as well. The hand is pointing to different points on the screen in images \ref{fig:pointLeftImage} and \ref{fig:pointRightImage}. However, the HOG outputs in \ref{fig:pointLeftHog} and \ref{fig:pointRightHog} are almost identical. This happens because the HOG algorithm mostly detects the outline of the hand and not the pointing finger which is facing mostly toward the camera. Because the HOG images are so similar, the regression does not train properly, causing the blue cursor in \ref{fig:pointLeftImage} and \ref{fig:pointRightImage} to be in the incorrect location.}
	\label{fig:close}
\end{figure*}

\begin{tabular}{|c|c|}
	\hline
	\multicolumn{2}{|c|}{\textbf{Errors for Convolution Neural Nets}}\\\hline
	\textbf{Regression Type} & \textbf{Average Error (Pixels)} \\\hline
	k-Nearest Neighbors & 47.8 \\\hline
	Linear Regression &  114.2 \\\hline	
\end{tabular}

\begin{tabular}{|c|c|}
	\hline
	\multicolumn{2}{|c|}{\textbf{Errors for Histogram of Oriented Gradients}} \\\hline
	\textbf{Regression Type} & \textbf{Average Error (Pixels)} \\\hline
	k-Nearest Neighbors & 32.0\\\hline
	Linear Regression & 79.7 \\\hline
	Combined & 47.0 \\\hline
\end{tabular}

\subsection{Evaluation as a Computer Interaction Device}
